### 2022-05-09 manuscript.Rmd
Add sensitivity analyses

documentclass     : "apa7"
classoption       : "man,donotrepeattitle"
fontsize          : "10pt"
output            : papaja::apa6_pdf
header-includes:
  - \geometry{a4paper}
  - \raggedbottom
  - \usepackage[all]{nowidow}
  - \usepackage{makecell}
  - \usepackage{setspace}
  - \DeclareCaptionLabelSeparator{bar}{ | }
  - \DeclareCaptionTextFormat{tabletext}{\textup{#1}}
  - \captionsetup[table]{font=small,labelfont=bf,labelsep=bar,textfont=bf,textformat=tabletext}
  - \captionsetup[figure]{belowskip=10pt,font=small,labelfont=bf,labelsep=bar,name=Fig.,textfont=normalfont}
---

@@

@@

# Run prior predictive simulation
dir.create(models_dir, showWarnings = FALSE)
res_prior <- brm(
  gi | se(sei) ~ 0 + Intercept + (1 | article / experiment),
  data = dat,
  prior = prior_c,
  sample_prior = "only",
  save_pars = save_pars(all = TRUE),
  chains = n_chains,
  iter = n_iter,
  warmup = n_warmup,
  cores = n_chains,
  control = list(adapt_delta = 0.99),
  seed = seed,
  file = here(models_dir, "res_prior"),
  file_refit = "on_change"
)
summary(res_prior)
# plot(res_prior)

# Run Bayesian multilevel model
res_brm <- update(
  res_prior,
  sample_prior = FALSE,
  file = here(models_dir, "res_brm"),
  file_refit = "on_change"
)
summary(res_brm)
# plot(res_brm)

@@

# Run prior predictive simulation
res_prior_reg <- brm(
  gi | se(sei) ~ 0 + Intercept + gender * age_c + task +
    (1 | article / experiment),
  data = dat,
  prior = prior_c,
  sample_prior = "only",
  save_pars = save_pars(all = TRUE),
  chains = n_chains,
  iter = n_iter,
  warmup = n_warmup,
  cores = n_chains,
  control = list(adapt_delta = 0.99),
  seed = seed,
  file = here(models_dir, "res_prior_reg"),
  file_refit = "on_change"
)
summary(res_prior_reg)
# plot(res_prior_reg)

# Run Bayesian multilevel model
res_brm_reg <- update(
  res_prior_reg,
  sample_prior = FALSE,
  file = here(models_dir, "res_brm_reg"),
  file_refit = "on_change"
)
summary(res_brm_reg)
# plot(res_brm_reg)

@@

# Run prior predictive simulation
res_prior_gender <- brm(
  gi | se(sei) ~ 0 + Intercept + (1 | article / experiment),
  data = dat_gender,
  prior = prior_c,
  sample_prior = "only",
  save_pars = save_pars(all = TRUE),
  chains = n_chains,
  iter = n_iter,
  warmup = n_warmup,
  cores = n_chains,
  control = list(adapt_delta = 0.99),
  seed = seed,
  file = here(models_dir, "res_prior_gender"),
  file_refit = "on_change"
)
summary(res_prior_gender)
# plot(res_prior_gender)

# Run Bayesian multilevel model
res_brm_gender <- update(
  res_prior_gender,
  sample_prior = FALSE,
  file = here(models_dir, "res_brm_gender"),
  file_refit = "on_change"
)
summary(res_brm_gender)
# plot(res_brm_gender)

>>>>

documentclass     : "apa7"
classoption       : "man,donotrepeattitle"
fontsize          : "10pt"
output            : papaja::apa6_pdf
header-includes:
  - \geometry{a4paper}
  - \raggedbottom
  - \usepackage[all]{nowidow}
  - \usepackage{makecell}
  - \usepackage{setspace}
  - \renewcommand{\arraystretch}{0.5}
  - \DeclareCaptionLabelSeparator{bar}{ | }
  - \DeclareCaptionTextFormat{tabletext}{\textup{#1}}
  - \captionsetup[table]{font=small,labelfont=bf,labelsep=bar,textfont=bf,textformat=tabletext}
  - \captionsetup[figure]{belowskip=10pt,font=small,labelfont=bf,labelsep=bar,name=Fig.,textfont=normalfont}
---

@@

# Re-run steps that take a long time?
run <- list(
  bayesian_models = FALSE,
  sensitivity_analysis = FALSE
)

@@

# Run prior predictive simulation
dir.create(models_dir, showWarnings = FALSE)
brms_file_refit <- ifelse(run$bayesian_models, "always", "never")
res_prior <- brm(
  gi | se(sei) ~ 0 + Intercept + (1 | article / experiment),
  data = dat,
  prior = prior_c,
  sample_prior = "only",
  save_pars = save_pars(all = TRUE),
  chains = n_chains,
  iter = n_iter,
  warmup = n_warmup,
  cores = n_chains,
  control = list(adapt_delta = 0.99),
  seed = seed,
  file = here(models_dir, "res_prior"),
  file_refit = brms_file_refit
)
summary(res_prior)
# plot(res_prior)

# Run Bayesian multilevel model
res_brm <- update(
  res_prior,
  sample_prior = FALSE,
  file = here(models_dir, "res_brm"),
  file_refit = brms_file_refit
)
summary(res_brm)
# plot(res_brm)

@@

# Run prior predictive simulation
res_prior_reg <- brm(
  gi | se(sei) ~ 0 + Intercept + gender * age_c + task +
    (1 | article / experiment),
  data = dat,
  prior = prior_c,
  sample_prior = "only",
  save_pars = save_pars(all = TRUE),
  chains = n_chains,
  iter = n_iter,
  warmup = n_warmup,
  cores = n_chains,
  control = list(adapt_delta = 0.99),
  seed = seed,
  file = here(models_dir, "res_prior_reg"),
  file_refit = brms_file_refit
)
summary(res_prior_reg)
# plot(res_prior_reg)

# Run Bayesian multilevel model
res_brm_reg <- update(
  res_prior_reg,
  sample_prior = FALSE,
  file = here(models_dir, "res_brm_reg"),
  file_refit = brms_file_refit
)
summary(res_brm_reg)
# plot(res_brm_reg)

@@

# Run prior predictive simulation
res_prior_gender <- brm(
  gi | se(sei) ~ 0 + Intercept + (1 | article / experiment),
  data = dat_gender,
  prior = prior_c,
  sample_prior = "only",
  save_pars = save_pars(all = TRUE),
  chains = n_chains,
  iter = n_iter,
  warmup = n_warmup,
  cores = n_chains,
  control = list(adapt_delta = 0.99),
  seed = seed,
  file = here(models_dir, "res_prior_gender"),
  file_refit = brms_file_refit
)
summary(res_prior_gender)
# plot(res_prior_gender)

# Run Bayesian multilevel model
res_brm_gender <- update(
  res_prior_gender,
  sample_prior = FALSE,
  file = here(models_dir, "res_brm_gender"),
  file_refit = brms_file_refit
)
summary(res_brm_gender)
# plot(res_brm_gender)

### 2022-05-09 supplement.Rmd
Add sensitivity analyses

```{r, sensitivity_analysis, eval=FALSE, include=TRUE}
# Re-run the meta-analysis for different values of r_assumed
seq(-0.9, 0.9, by = 0.3) %>%
  set_names(., str_c("r = ", print_num(.))) %>%
  map(function(ri_sens) {

@@

    # Re-run meta-analysis
    update(res_brm, newdata = dat_ri_sens, refresh = 0)
  }) -> res_ri_sens

# Prior sensitivity analysis
list(
  "Intercept U(-10,10)" = c(
    set_prior("uniform(-10, 10)", class = "Intercept"),
    set_prior("cauchy(0, 0.3)", class = "sd")
  ),
  "Intercept N(0,0.2)" = c(
    set_prior("normal(0, 0.2)", class = "Intercept"),
    set_prior("cauchy(0, 0.3)", class = "sd")
  ),
  "SD U(0,10)" = c(
    set_prior("normal(0, 1)", class = "Intercept"),
    set_prior("uniform(0, 10)", class = "sd")
  ),
  "SD Student-t(10,0,0.2)" = c(
    set_prior("normal(0, 1)", class = "Intercept"),
    set_prior("student_t(10, 0, 0.2)", class = "sd")
  )
) %>%
  # Re-run the meta-analysis with different priors
  map(
    function(prior_sens) update(res_brm, prior = prior_sens, refresh = 0)
  ) -> res_prior_sens

# Create a table summarizing all sensitivity analyses
map2_dfr(
  c(res_ri_sens, res_prior_sens),
  c(names(res_ri_sens), names(res_prior_sens)),
  function(res, name) {

    # Compute ICC
    var_experiment <- as.matrix(
      res,
      variable = "sd_article:experiment__Intercept"
    )^2
    var_article <- as.matrix(
      res,
      variable = "sd_article__Intercept"
    )^2
    var_total <- var_experiment + var_article
    icc <- var_article / var_total
    icc_row <- mean_qi(icc) %>%
      rename(Estimate = y, `l-95% CI` = ymin, `u-95% CI` = ymax)

    # Create a data frame row of summary statistics
    with(summary(res), bind_rows(fixed, bind_rows(random))) %>%
      bind_rows(icc_row) %>%
      transmute(
        parameter = c("Hedges' g", "SD_{article}", "SD_{experiment}", "ICC"),
        Estimate = print_ci(Estimate, `l-95% CI`, `u-95% CI`)
      ) %>%
      pivot_wider(names_from = parameter, values_from = Estimate) %>%
      bind_cols(Simulation = name, .)
  }
) -> tab_sens

# Display the table
apa_table(
  tab_freq,
  caption = "Sensitivity analyses",
  font_size = "scriptsize"
)

# Save the table
write_csv(tab_sens, file = here(tables_dir, "sensitivity.csv"))
```

>>>>

```{r, sensitivity_analysis}
# Re-run the sensitivity analyses only if requested
if (run$sensitivity_analysis) {

  # Re-run the meta-analysis for different values of r_assumed
  seq(-0.9, 0.9, by = 0.3) %>%
    map_dfr(function(ri_sens) {

@@

      # Re-run meta-analysis
      res <- update(res_brm, newdata = dat_ri_sens, refresh = 0)

      # Re-run meta-regression
      res_reg <- update(res_brm_reg, newdata = dat_ri_sens, refresh = 0)

      # Return both as a tibble together with the label
      return(
        tibble(
          manipulation_value = str_c("$r = ", print_num(ri_sens), "$"),
          res = list(res),
          res_reg = list(res_reg),
        )
      )
    }) %>%
    bind_cols(
      manipulation_name = c("Assumed correlation", rep("", nrow(.) - 1)), .
    ) -> res_ri_sens

  # Prior sensitivity analysis
  list(
    `$b_Intercept\\sim\\mathcal{U}(-10,10)$` = c(
      set_prior("uniform(-10, 10)", class = "b", coef = "Intercept"),
      set_prior("normal(0, 0.5)", class = "b"),
      set_prior("cauchy(0, 0.3)", class = "sd")
    ),
    `b\\sim$\\mathcal{N}(0,0.2)$` = c(
      set_prior("normal(0, 0.2)", class = "b", coef = "Intercept"),
      set_prior("normal(0, 0.5)", class = "b"),
      set_prior("cauchy(0, 0.3)", class = "sd")
    ),
    `$\\sigma\\sim\\mathcal{U}(0,10)$` = c(
      set_prior("normal(0, 1)", class = "b", coef = "Intercept"),
      set_prior("normal(0, 0.5)", class = "b"),
      set_prior("uniform(0, 10)", class = "sd")
    ),
    `$\\sigma\\sim\\text{Student-}t(10,0,0.2)$` = c(
      set_prior("normal(0, 1)", class = "b", coef = "Intercept"),
      set_prior("normal(0, 0.5)", class = "b"),
      set_prior("student_t(10, 0, 0.2)", class = "sd")
    )
  ) %>%
    map2_dfr(names(.), function(prior_sens, prior_name) {

      # Re-run meta-analysis of mental rotation performance
      res <- update(res_brm, prior = prior_sens, refresh = 0)

      # Re-run meta-regression of mental rotation performance
      res_reg <- update(res_brm_reg, prior = prior_sens, refresh = 0)

      # Re-run meta-analysis of gender differences
      res_gender <- update(res_brm_gender, prior = prior_sens, refresh = 0)

      # Return both as a tibble together with the label
      return(
        tibble(
          manipulation_value = prior_name,
          res = list(res),
          res_reg = list(res_reg),
          res_gender = list(res_gender)
        )
      )
    }) %>%
    bind_cols(
      manipulation_name = c("Prior specification", rep("", nrow(.) - 1)), .
    ) -> res_prior_sens

  # Combine results from all sensitivity analyses
  res_sens <- bind_rows(res_ri_sens, res_prior_sens)

  # Backup for reuse
  saveRDS(res_sens, here(models_dir, "res_sens.rds"))
} else {
  # Otherwise we load the pre-fitted models
  res_sens <- readRDS(here(models_dir, "res_sens.rds"))
}
```

\renewcommand{\arraystretch}{1.0}

```{r, tabs5, include=TRUE}
# Helper functions for printing results as a table
print_res_table <- function(res, label_1, label_2) {
  spread_draws(res, `b_.*`, `sd_.*`, regex = TRUE, ndraws = NULL) %>%
    transmute(
      `Hedges $g$` = b_Intercept,
      `$\\sigma_\\text{article}^2$` = sd_article__Intercept^2,
      `$\\sigma_\\text{experiment}^2$` = `sd_article:experiment__Intercept`^2,
      `${ICC}$` = `$\\sigma_\\text{article}^2$` /
        (`$\\sigma_\\text{article}^2$` + `$\\sigma_\\text{experiment}^2$`)
    ) %>%
    summarize(across(.fns = mean_qi)) %>%
    map_dfc(~ print_ci(.$ymin, .$ymax, mean = .$y)) %>%
    bind_cols(Manipulation = label_1, ` ` = label_2, .)
}

# Combine results for the (main) meta-analysis of mental rotation performance
tab_sens <- res_sens %>%
  select(res, manipulation_name, manipulation_value) %>%
  pmap_dfr(function(res, manipulation_name, manipulation_value) {
    print_res_table(res, manipulation_name, manipulation_value)
  })

# Display the table
apa_table(
  tab_sens,
  caption = "Sensitivity analyses for the meta-analysis of mental rotation performance",
  font_size = "scriptsize", escape = FALSE
)

# Save the table
write_csv(tab_sens, file = here(tables_dir, "tabs5_sens.csv"))
```

```{r, tabs6, include=TRUE}
# Helper functions for printing results as a table
print_res_reg_table <- function(res_reg, label_1, label_2) {
  spread_draws(res_reg, `b_.*`, `sd_.*`, regex = TRUE, ndraws = NULL) %>%
    transmute(
      `Hedges $g$` = b_Intercept,
      `Female - mixed` = b_gender2M1,
      `Male - female` = b_gender3M2,
      `Age (per year)` = b_age_c,
      `Habituation - VoE` = b_task2M1,
      `[Female - mixed] × age` = `b_gender2M1:age_c`,
      `[Male - female] × age` = `b_gender3M2:age_c`
    ) %>%
    summarize(across(.fns = mean_qi)) %>%
    map_dfc(~ print_ci(.$ymin, .$ymax, mean = .$y)) %>%
    bind_cols(Manipulation = label_1, ` ` = label_2, .)
}

# Combine results for the meta-regression of mental rotation performance
tab_sens_reg <- res_sens %>%
  select(res_reg, manipulation_name, manipulation_value) %>%
  pmap_dfr(function(res_reg, manipulation_name, manipulation_value) {
    print_res_reg_table(res_reg, manipulation_name, manipulation_value)
  })

# Display the table
apa_table(
  tab_sens_reg,
  caption = "Sensitivity analyses for the meta-regression of mental rotation performance",
  font_size = "scriptsize", landscape = TRUE, escape = FALSE
)

# Save the table
write_csv(tab_sens_reg, file = here(tables_dir, "tabs6_sens_reg.csv"))
```

```{r, tabs7, include=TRUE}
# Combine results for the meta-analysis of gender differences
tab_sens_gender <- res_sens %>%
  filter(!map_lgl(res_gender, is.null)) %>%
  select(res_gender, manipulation_name, manipulation_value) %>%
  pmap_dfr(function(res_gender, manipulation_name, manipulation_value) {
    print_res_table(res_gender, manipulation_name, manipulation_value)
  })

# Display the table
apa_table(
  tab_sens_gender,
  caption = "Sensitivity analyses for the meta-analysis of gender differences",
  font_size = "scriptsize", escape = FALSE
)

# Save the table
write_csv(tab_sens_gender, file = here(tables_dir, "tabs7_sens_gender.csv"))
```
